E Coli Project Paper Incredibly Rough Draft

### 2013-09-29 paper/paper.tex
pulled from dr roundy, add some things Tested everything on crystal.
Fixed wall bug in arrow plots and paper Tested everything on node37.

\subsection{Triangular Shapes}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-500-300-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-360-480-600-1500}
  \caption{Total protein fluctuation in the right, middle, and left
    parts of a equilateral (top), iscoscolese (middle), and 3-4-5
    (bottom) triangle.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{total-oscillation-triangle-plot}
\end{figure}

@@

\end{figure}
\subsubsection{Randst-96-Star}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  \caption{Total protein fluctuation in the star cell shape.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{total-oscillation-randst-96-plot}
\end{figure}

>>>>

\subsection{Triangular Shapes}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
  \caption{Total protein fluctuation in the right, middle, and left
    parts of a equilateral (top), iscoscolese (middle), and 3-4-5
    (bottom) triangle.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{total-oscillation-triangle-plot}
\end{figure}

@@

\end{figure}
\subsubsection{Randst-94-mannik shape}
\begin{figure}
  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1100-1100-9500-1500.pdf}
  \includegraphics[width=2.8cm]{../mannik-1.png}
  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1300-2000-9400-1500.pdf}
  \includegraphics[width=2.8cm]{../mannik-2.png}
  \caption{Arrow plots for our simulation and mannik's experimental}
  \label{arrow-randst-94}
\end{figure}

\subsubsection{Randst-96-Star}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  \caption{Total protein fluctuation in the star cell shape.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{total-oscillation-randst-96-plot}
\end{figure}
